\input{Common/Common.tex}

\begin{document}

\section*{Questionnaire}

\subsection*{Personal details}

Please tell us some personal information:
\begin{itemize}
\item[Age:] \underline{\hspace{2cm}}
\item[Gender:] \underline{\hspace{2cm}}
\end{itemize}

Please state your experience with robots:
\begin{itemize}
\item[$\ocircle$] I have worked with robots before.
\item[$\ocircle$] I have interacted with robots before.
\item[$\ocircle$] I have seen robots in reality or on television.
\item[$\ocircle$] I am unfamiliar with robots.
\end{itemize}

\pagebreak

\subsection*{Physical safety}
Please rate how critical you would consider the following physical hazards, considering only physical harm to people:\\
\likertquestion[Safe][Dangerous]{The gas oven in the kitchen has been left on accidentally.}
\likertquestion[Safe][Dangerous]{The wall socket power switches in the kitchen have been left on accidentally.}
\likertquestion[Safe][Dangerous]{The Pepper robot is overheating.}

\pagebreak

\subsection*{Robot rating}
Using the scale provided, how closely do you associate the following attributes with \robot?%
\begin{center}
\begin{table}[h]
  \centering
    \csvreader[RSscale]{RoSAS/RoSAS-items.csv}{}%
    {\csvcoli & $\ocircle$ & $\ocircle$ & $\ocircle$ & $\ocircle$ & $\ocircle$ & $\ocircle$ & $\ocircle$}%
\end{table}
\end{center}
\pagebreak

\subsection*{Robot rating}
Please rate your impression of \robot{} on these scales:%
\begin{center}
\begin{table}[h]
  \centering
    \csvreader[GSscale]{GodSpeed/GodSpeed-items.csv}{}%
    {\csvcoli & $\ocircle$ & $\ocircle$ & $\ocircle$ & $\ocircle$ & $\ocircle$ & \csvcolii}%
\end{table}
\end{center}

\subsection*{Emotional state}
Please rate your own emotional state on these scales:
\begin{center}
\begin{table}[h]
  \centering
    \csvreader[GSscale]{GodSpeed/GodSpeed-items-estate.csv}{}%
    {\csvcoli & $\ocircle$ & $\ocircle$ & $\ocircle$ & $\ocircle$ & $\ocircle$ & \csvcolii}%
\end{table}
\end{center}

\pagebreak

\subsection*{Robot safety}
Please state how much you agree with the following statements based on your interaction with \robot{}:\\
\likertquestion{\robot{} can identify hazards accurately and reliably.}
\likertquestion{\robot{} can accurately judge when a situation requires human intervention.}
\likertquestion{\robot{} requests human intervention when not needed.}
\likertquestion{\robot{} does not request human intervention when it is needed.}
\likertquestion{\robot{} is likely to make the home environment safer.}
\likertquestion{\robot{} will have no effect on the safety of the home environment.}

\pagebreak

\subsection*{Robot sociability}
Please state how much you agree with the following statements regarding your interaction with \robot{}:\\
\likertquestion{\robot{} acted in a socially appropriate way.}
\likertquestion{\robot{} itself seemed socially aware.}
\likertquestion{\robot{} was malfunctioning at some point.}
\likertquestion{\robot{} was irritating on purpose.}

\pagebreak

\subsection*{Comments}
\openquestion{When prompted by \robot{} to turn off the oven, why did you/did you not choose to do this?}\\
\openquestion{When prompted by \robot{} to turn off the power switches, why did you/did you not choose to do this?}\\
\openquestion{When prompted by \robot{} to relax Pepper's joints, why did you/did you not choose to do this?}\\
\openquestion{Do you have any general impressions about \robot{} during your interaction with it?}\\
\openquestion{Do you have any questions you would like to ask us?}
\end{document}
